---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# evabic

```{r, echo = FALSE}
version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])                                                              
version <- gsub('-', '.', version)
```

<!-- badges: start -->
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg?style=flat-square)](commits/master)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)
<!-- badges: end -->

The goal of evabic is to provide handy functions to evaluate binary classifiers.

## Installation


You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("abichat/evabic")
```
## Example

Suppose that you are testing 10 conditions: `A, B, C, D, E, F, G, H, I, & J`.

Conditions `A` to `E` are in H0 and conditions `F` to `J` are in H1.

Your model detect `D` and `G` to `I` in H1.

```{r}
conditions <- LETTERS[1:10]
trueH1 <- LETTERS[6:10]
detectedH1 <- c("D", LETTERS[7:9])
```

```{r example}
library(evabic)
```

```{r}
ebc_TP(detectedH1, trueH1)
ebc_TPR(detectedH1, trueH1)
ebc_ACC(detectedH1, trueH1, all = conditions)
```

```{r}
ebc_tidy(detectedH1, trueH1, m = 10, measures = c("ACC", "TPR", "FDR", "F1"))
```




